---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/"
)
```


# TailorBayes

<!-- badges: start -->
[![Build Status](https://travis-ci.org/solonkarapa/TailorBayes.svg?branch=master)](https://travis-ci.org/solonkarapa/TailorBayes)
[![codecov](https://codecov.io/gh/solonkarapa/TailorBayes/branch/master/graph/badge.svg)](https://codecov.io/gh/solonkarapa/TailorBayes)

Contains functions to perform Tailored Bayesian inference for binary classification.   Markov Chain Monte Carlo (MCMC) is used to simulate the posterior. The output is a 'coda' mcmc object that can then be summarised using the [coda](https://cran.r-project.org/web/packages/coda/index.html) package or similar ones. 

## Installation

```{r, eval = FALSE}
# Install from GitHub
devtools::install_github("solonkarapa/TailorBayes")
```

## Usage

Get started with

```{r, eval = FALSE}
library(TailorBayes)
```

The main function of the package is `metrop_tailor()`

```{r, eval = FALSE}
# Run to see the function documentation
?metrop_tailor
```

A vignette on using the package 

```{r, eval = FALSE}
# Run to see the vignette
browseVignettes("TailorBayes")
```

Cite as 

```{r, eval = F}
citation("TailorBayes")
```


